---
title: "Mtcars and shiny"
output: html_document
---

```{r}
library(shiny)
library(ggplot2)
library(plotly)
```


##1. Introduction
This is a shiny presentation using "mtcars database. There are three tab panels: the first one creates a histogram from a chosen variable; the second one combines two variables producing a two dimension graphic; the third one provides a statistical summary.

##2. Shiny App
###2.1 Histograms
To create an histogram I've used ggplot and plotly. The user can choose any variable from database. Let's see an example with the plotly library

```{r}
a<-qplot(mpg, data=mtcars)
a

```

###2.2 Two variable scatterplot
In this tab panel the user can choose two variables from mtcars dataset. Automatically, there is a scatterplot of these two variables.

```{r}
plot(mtcars$mpg, mtcars$disp)
```


###2.2 Statistical summary
In this tab panel the user can select from a checkbox the variables he/she wants to incorporate to the summary.

```{r}
summary(mtcars$mpg)
```


##3 Conclusion
The advantage of shiny application is its interactivity, and the user easily can choose different graphics and variables.